---
title: "p8105_hw1_fw2394"
author: "Fang Wang"
date: "2024-09-15"
output: github_document
---

# Homework 1

## Problem 1

**I loaded necessary package "tidyverse":**
```{r libraries}
library(tidyverse)
```

**I loaded the dataset "penguins":**
```{r dataset_loading}
data("penguins", package = "palmerpenguins")
```

**To get all variables in penguins:**
```{r variables}
str(penguins)
```
**The "penguins" dataset includes 8 variables: "species", "island",  "bill_length_mm", "bill_depth_mm", "flipper_length_mm", "body_mass_g", "sex", "year".**

**To see the data size:**
```{r data_size}
nrow(penguins) 
ncol(penguins)
```
**The dataset has 344 rows and 8 columns.**

**To check the mean of flipper length:**
```{r mean_filpper_length}
summary(penguins $ flipper_length_mm)
# Alternatively:
mean(penguins$flipper_length_mm, na.rm=TRUE)
```
**The mean of flipper length is 200.9mm.**

**To make a scatterplot using ggplot:**
```{r scatterplot}
ggplot(penguins, aes(y = flipper_length_mm, 
                     x = bill_length_mm,
                     color = species)) + 
  geom_point()
```

**To save the scatterplot:**
```{r save}
ggsave("penguins_plot.png", dpi = 300)
```


## Problem 2

**To create a random sample of size 10 from a standard normal distribution:**
```{r random_sample}
set.seed(0653)  # Set seed for reproducibility
random_sample <- rnorm(10)
```

**To create a logical vector to indicate whether elements are greater than 0:**
```{r logical_vector}
logical_vector <- random_sample > 0
```

**To create a character vector of length 10:**
```{r character_vector}
character_vector <- c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J")
```

**To create a factor vector of length 10, with 3 different "levels":**
```{r factor_vector}
factor_vector <- factor(rep(c("Level1", "Level2", "Level3"), length.out = 10)) # using rep() to repeat 3 levels
```

**To combine all into a data frame:**
```{r df}
dataframe <- data.frame(
  random_sample = random_sample,
  logical_vector = logical_vector,
  character_vector = character_vector,
  factor_vector = factor_vector
)
```

**To print the whole dataframe:**
```{r print}
print(dataframe) 
```

**To calculate the mean of the random sample:**
```{r mean_sample}
mean_sample <- dataframe |>
  pull(random_sample) |>
  mean(na.rm=TRUE)
```
**It works to calculate the mean of the random sample.**

**To calculate the mean of the logical vector:**
```{r mean_logical}
mean_logical <- dataframe |>
  pull(logical_vector) |>
  mean(na.rm=TRUE)
```
**It works to calculate the mean of the logical vector.**

**To calculate the mean of the character vector:**
```{r mean_character}
mean_character <- dataframe |>
  pull(character_vector) |>
  mean(na.rm=TRUE)
```
**It doesn't work to calculate the mean of the character vector.**

**To calculate the mean of the factor vector:**
```{r mean_factor}
mean_factor <- dataframe |>
  pull(factor_vector) |>
  mean(na.rm=TRUE)
```
**It doesn't work to calculate the mean of the factor vector.**
